\section{Budgeting}
\label{sec:budgeting}
% !TeX spellcheck = en_US

Here is a short explanation on budgeting:
\begin{quote}\small
	The process or definition of budgeting is the act of creating a plan to spend your money.
	Creating this spending plan allows you to determine in advance whether you will have enough money to do the things you need to do or would like to do.\footnote{Cp. \url{https://www.mymoneycoach.ca/budgeting/}.}
\end{quote}

\subsection{Motivation for Creating a Budget}
\label{subsec:motivation-creating-budget}

Why should you budget? A budget will help you plan for short-term expenses such as your monthly bills; mid-term expenses such as vacations; and long-term expenses such as buying a house, paying for a child’s college education or putting away money for retirement.
When you have an app, spreadsheet or notebook in front of you showing how much money you expect to make over the one month, six months, one year or five years --- and how much of that money will be flowing out and how much you will have left to save each month --- you’ll always know when you need to cut back on spending, when you can afford to loosen the reins and how long it will take to save for major goals or pay off debts.
If you’re not happy with the numbers, knowing what they are will help you take steps to improve your situation.
These steps might include paying off credit cards to increase your monthly cash flow; reducing your food expenses; or getting a promotion, switching companies, starting a side hustle or founding your own full-time business to make more money.\footnote{Taken verbatim from \url{https://www.investopedia.com/university/budgeting/basics1.asp}.}

So all in all, if you want to, you can plan your future spending so that you know when your planned expenses might exceed your planned income.
If you want to, you can plan for future expenses such as a vacation, on top of the rather usual expenses such as buying groceries, clothes and the monthly payment on your car lease.

\begin{specialnote}
	If you are not interested in budgeting by now, please skip this section and continue with \autoref{sec:editing-finances.ods}, \autopageref{sec:editing-finances.ods}.
\end{specialnote}

\subsection{Budgeting in Finances.ods}
\label{subsec:budgeting-in-finances.ods}

\subsubsection{Budgeting Basics}
\label{subsubsec:budgeting-basics}

As mentioned in \autoref{subsec:first-things-first}, if you like to budget your income and expenses, you need to use the budgeting sheets for this.
It is possible to create lots of different budget items which essentially represent either incoming or outgoing cash flows.
In other words, you can budget practically any kind of cash flow, regardless if you expect it to receive or spend any cash amount in the future.

As outlined in a few paragraphs above, the file work with the approach that you plan your budget tailored to your needs.
To do so, you could start by writing down a list that consists of all the expenses that occur every month or every few months.
Then write down one-time expenses like a vacation, or a new winter coat or car.
Then you should decide on \begriff{when} you plan to buy something.

So this is a process which implies that you plan your expenses beforehand.
Not perfectly and/or entirely, but definitely to the best of your abilities at that point in time.
And you definitely ought to rework these plans if complications or uncertainties come to light.
And the budget as a whole gets more and more optimized to achieve the desired goals, work with the prioritized expense categories at the right time, account for relatively high one-time/emergency expenses and so forth.

\subsubsection{Budgeting for One Year}
\label{subsubsec:budgeting-for-one-year}

As mentioned in \autoref{subsec:first-things-first} and \autoref{subsec:tracking-column-date}, \tfn is created to be used for one calendar year.
There is nothing speaking against using the file for multiple (consecutive) years, except that the formulas that are built into it only check for the right month and day, thus rendering the calculated sums per month meaningless.

\subsubsection{The Envelope Method}
\label{subsubsec:budgeting-the-envelope-method}

The budgeting principle that is used in \tfn is the envelope method.
If you would like to know more about this way of budgeting, please visit your favorite search machine, but a short introduction can be found on \href{https://en.wikipedia.org/wiki/Envelope_system}{wikipedia}\footnote{URL: \href{https://en.wikipedia.org/wiki/Envelope_system}{https://en.wikipedia.org/wiki/Envelope{\_}system}.}.
The system is of relevance if you are either unable or unwilling to buy the item in this very moment, \ie you plan to buy it in a few weeks or months.
Then the envelope method works like this:
\begin{enumerate}
	\item You write the name and total cost of an expense onto an envelope.
	\item Ideally, you put a fixed amount into the envelope each month.
	If you are not able to, you put any amount you wish anytime into the envelope.
	\item When the worth in the envelope reaches the values written on it, you can take it out.
\end{enumerate}
First of, the principle is obviously used in its digital or virtual form, as there is no envelope being used within the file but the principle is adhered to nonetheless.
Secondly, it was ``enhanced'' with dates being used.

The key to translating the envelope method to a virtual perspective is that the envelope could be interpreted as an extra budgeting account you could put your money into.
You have two choices:
\begin{enumerate}
	\item The money may remain in whatever account you have included in the tracking.
	\item You could transfer some amount \( X \) for a month with budgeted items (which would be practically every month) to that virtual envelope, \ie some kind of special account for budgeting needs.
\end{enumerate}

To clarify the second choice and its implications:
\begin{itemize}
	\item One would need to have a spare account.
	\item One would need to perform the necessary calculations to get the right amount for the month.
	\item Ultimately, one would need to process all these arguably small money transfers for the amounts for budgeted items which would be due that month.\footnote{And transferring them in bulk would definitely lead to the system being to inflexible, since you would have to answer the questions of timing and the composition (which items would have to be included) for a transfer.}
\end{itemize}
All in all, it is probably best to let that topic rest.

\subsubsection{Deviation}
\label{subsubsec:budeting-deviation}

First of, \begriff{Deviation} in the context of budgeting and \tfn is to be understood as the difference between the planned amount of an expense and its real-world amount.
The file automatically computes the surplus or deficit each month.

Secondly, the formulas in the budgeting sheets work this way:
\begin{enumerate}
	\item They look for the budgeted total in a category in month \( M \).
	Let us imagine we are dealing with the category clothing \& accessoires:
	\begin{itemize}
		\item The budgeted amount for a new pair of shoes is 70\,€.
		\item The budgeted amount for a new jacket is 100\,€.
	\end{itemize}
	This makes a budgeted total of 170\,€ for that month \( M \).
	\item Once month \( M \) is over, you are in month \( M+1 \).
	Because you do the tracking, \tfn also is aware of what you actually spent on that new pair of shoes and your new jacket in \( M \).
	The amount for both items is totaled.
	\item This value is then compared to the budgeted total from before, \ie 170\,€.
\end{enumerate}

A look at the possible outcomes of that comparison:
\begin{itemize}
	\item If the budgeted total and the spent total equal each other, the deviation obviously equals 0 as well.
	\item If the amount spent is larger, \eg 190\,€, than the budgeted 170\,€, the deficit \( 190-170 \) = 20\,€ will be subtracted from the budget of the following month \( X+1 \).
	Perhaps view this as a \begriff{penalty}.
	\item Vice versa, if you spent 150\,€, you made a surplus of \( 170-150 = 20 \)\,€, which goes into the budget of month \( X+1 \).
	This is a \begriff{reward}. :)
\end{itemize}

Thirdly, this process outlined above happens every month, especially for future months, which is crucial for creating the budget.
When you have finished writing down the details for your expense item, you will notice that the ``header'' up top will change.
It automatically shows you the \emph{planned} difference between the expenses and income of the months to come.
\begin{specialnote}
	While you work on your budget items, you will notice that the cells up top change.
	This is extremely important to understand: this is real-time feedback in regards to your budgeting.
	If you budget too strongly against your available funds, you essentially make a plan to overspend, hence you will accrue debt and the header will reflect that.
	In this case, you should change your plan accordingly.
\end{specialnote}

\subsection{Budgeting for Expenses}
\label{subsec:budgeting-expenses}

This subsection gives a step-by-step guide on what is required to budget for an expense.
Additional remarks and relatively deeper thoughts are to be found in \autoref{subsec:thoughts-on-budgeting}, \autopageref{subsec:thoughts-on-budgeting}.

To budget for an expense, you need to navigate to the sheet \sheetname{BudgetEXPItems}.
You will observe there are gray cells to be found.
As mentioned in \autoref{subsec:introduction-something-technical}, they are not to be edited.
Furthermore, an important note for this sheet:
\begin{specialnote}
	Do not edit the cells to the right of the gray cells.
\end{specialnote}

For creating a new entry for an expense, you need to gather some details which are to be filled into columns.
These columns have the magical name \ac{bic} and can be interpreted as steps you need to take to create a budget.
For that, you should read through \autoref{subsubsec:budgeting-item-column-number} to \autoref{subsubsec:budgeting-item-column-category}.
It is important that you fill out \emph{all} columns!
Well, except the first one, actually.

\subsubsection{BIC: Number}
\label{subsubsec:budgeting-item-column-number}

This the optional step: enumerate the item you are about to add.
I suggest that you do as you may want to rearrange the items later on.
Also, who doesn't like a well-sorted list?? :)

\subsubsection{BIC: Description}
\label{subsubsec:budgeting-item-column-description}

Just name the item, perhaps give a few details.

\subsubsection{BIC: Amount}
\label{subsubsec:budgeting-item-column-amount}

In short: enter the amount you plan to allocate to the item.
If you are about to enter data for an expense item with multiple payments for a time period longer than 1 month, you have 2 possibilities:
\begin{enumerate}
	\item You enter the total amount for the year and let \tfn do the work to have it spread out evenly from start to end.
	\item Or you enter multiple time periods with different kinds of lengths and amounts to ultimately have the right total for all the payments over the desired time period.
	There are so many ways you can choose to do this
\end{enumerate}

\subsubsection{BIC: Start Date}
\label{subsubsec:budgeting-item-column-start-date}

Enter the start date you want to begin budgeting for that item.
The date you enter must have the format \programmcode{YYYY-MM}, like the dates in the tracking sheets (see \autoref{subsec:tracking-column-date}, \autopageref{subsec:tracking-column-date}).

\subsubsection{BIC: End Date}
\label{subsubsec:budgeting-item-column-end-date}

Enter the end date in which you plan to purchase the item or the monthly expense stops.
The date you enter must have the format \programmcode{YYYY-MM}, \eg \programmcode{2019-09} which stands for September 2019.

\subsubsection{BIC: Monthly Expense}
\label{subsubsec:budgeting-item-column-monthly-expense}

The \ac{bic} titled \begriff{monthly expense} is for the following distinction:
\begin{itemize}
	\item If the expense item consist of a single purchase/item/money transfer, you need to set the value to \programmcode{No}.
	An example would be the purchase of a winter coat or a car.
	\item If the item is an expense that you actually spend money on in multiple months throughout the year, you need to set the value to \programmcode{Yes}.
	An example would be paying for \eg utilities, such as water, electricity etc., on multiple occasions throughout the year.
\end{itemize}

There is also a clarification to be made about reoccurring expenses which are at intervals that do not equal a month's length.
This will be elaborated on in \autoref{subsubsec:thoughts-non-monthly-expenses}, \autopageref{subsubsec:thoughts-non-monthly-expenses}.

\subsubsection{BIC: Sum Prohibition}
\label{subsubsec:budgeting-item-column-sum-prohibition}

This \ac{bic} is for prohibiting if the amount for an expense item is to be summed up or not.

First of, please take note of this:
\begin{specialnote}
	The column/switch \begriff{sum prohibition} only has an effect if the time period is longer than 1 month.
	If the time period does not encompass at least 2 months, there is no division and thus no summation, as already mentioned in \autoref{subsubsec:budgeting-the-envelope-method}.
\end{specialnote}

So\ldots should you fill in \programmcode{Yes} or \programmcode{No}?
\begin{itemize}
	\item Put \programmcode{Yes} if you want to prevent the summation.
	This makes sense if the item's time period is \emph{longer} than 1 month, which happens typically if it is a monthly expense.
	\item Put \programmcode{No} if you want the amount to put summed up in the last month.
	This makes sense if the expense is a one-time purchase.
\end{itemize}
There obviously are more use cases than listed above.

You must put \programmcode{Yes} here if you have a monthly expense, otherwise all the amounts per month get summed up to their total in the last month, which would lead to strong deviations in each of the relevant months.

But you might be wondering why there is such a column which serves to prohibit summation of the budgeted amount in the first place.
Well, this column mostly exists because of the limitations that I ran into with using spreadsheet software and, frankly speaking, the way I conceptualized budgeting over multiple months.
I do not know whether I solved the problem in the best way possible, but it certainly works for dealing with ``taking the money out of the (digital) envelope'' which is the inherent characteristic to the envelope method (see \autoref{subsubsec:budgeting-the-envelope-method}, \autopageref{subsubsec:budgeting-the-envelope-method} for more information).
Because, as described in \autoref{subsubsec:budgeting-item-column-monthly-expense}, there are also monthly expenses, which are not to be\todo{weiter}

The way \tfn works is that with each month, it stays true to the envelope method.
At the end, one would take all the money for that out of that envelope because if you add up all the monthly values, you end up with 800\,€.
At this point in time, the expense item is \begriff{budgeted} and can be purchased/billed.
As you will observe, if you budget an entry for a time period longer than 1 month, the amount gets divided evenly by the number of months, \ie the length of the time period.
If you budget 500\,€ for 5 months, the formulas in \tfn automatically put 100\,€ into the virtual envelope in each month of the 5 months, which all in all makes up the 500\,€.

Please do read \autoref{subsec:examples-budgeting-expenses} starting on \autopageref{subsec:examples-budgeting-expenses} for more clarification.\todo{lassen?}

\subsubsection{BIC: Done}
\label{subsubsec:budgeting-item-column-budgeted}

This column serves to enter if the budget item has been bought or not.
You could utilize this column to represent some kind of to-do list.
\begin{itemize}
	\item Put \programmcode{Yes} if the purchase/expense has been made.
	\item Put \programmcode{No} if not.
\end{itemize}

\subsubsection{BIC: Category}
\label{subsubsec:budgeting-item-column-category}

The column \begriff{Category} is pretty straight forward.
You will have to provide the category the expense is to be attributed to.
You can only select a category that is provided by the drop-down list that is programmed to this cell.
To see the valid entries, press \keystroke{Alt}+\keystroke{\( \downarrow \)} or right-click on the cell and then click on \programmcode{Selection List}.


\subsection{Budgeting for Income}
\label{subsec:budgeting-income}

This very subsection of the guide simply exists if you, the reader, decided to read up on budgeting for income.
Because once you understood how to budget for an expense, you have the knowledge to budget for an income item as well.
At this point, I do not think there is anything new to explain in regards to budgeting income items.
You would simply have go to the sheet \sheetname{BudgetINCitems} and do it in an analogical way.

\subsection{Thoughts on Budgeting}
\label{subsec:thoughts-on-budgeting}

What about reality, when things go up, down, sideways or in circles?
Life can be a mess and if you really want to use \tfn for tracking and budgeting your cash, I would like to support that by providing some help in the form of thoughts.

\subsubsection{Thoughts on Non-Monthly Expenses}
\label{subsubsec:thoughts-non-monthly-expenses}

This part is in regards to \autoref{subsubsec:budgeting-item-column-monthly-expense}, where reoccurring expenses that are to be paid at non-monthly intervals (\eg quarterly) were mentioned.
There are further elaborations to be made on the possibilities of non-monthly expenses.
\begin{itemize}
	\item You can set their start and end date to span over the whole year (or 12 months): the expense item would occur after 12 months and it would be the total of all single payments.
	There would be a deviation in all months, but the yearly total deviation equals 0.
	Obviously, as it is a reoccurring expense, the switch for \begriff{sum prohibition} would have to be set to \programmcode{Yes}.
	\item For each payment, \ie the expense is regarded as a single purchase and needs the \begriff{sum prohibition} switch set to \programmcode{No}.
	Hence one would have to create multiple entries for the whole group of quarterly payments.
	There are 2 possibilities one could choose:
	\begin{enumerate}
		\item One could set the start date for all payments to the month of today or whenever one would want to start budget for it.
		Note: this would lead to an increased budgeting load in the ensuing months right after the start date.
		So this would lead to 4 quarterly budget items, all of which start in \programmcode{2019-01}, but end in \programmcode{2019-03}, \programmcode{2019-06}, \programmcode{2019-09} and \programmcode{2019-12}.
		\item One could set the start date to the month after a payment happened.
		Explanation: let us assume the first payment would be due in march, thus the time period would be \programmcode{2018-01} to \programmcode{2018-03}.
		Accordingly, the next budget item could start in \programmcode{2018-04} and end it \programmcode{2019-06}.
	\end{enumerate}
\end{itemize}

\subsubsection{Thoughts on Different Dates in Real Life}
\label{subsubsec:thoughts-different-dates}

Dates in regards to planned expenses can differ from how events unfold in reality.
\begin{itemize}
	\item What if\ldots when you just want to buy an item earlier than planned?
	\item What if\ldots when you somehow end up buying something later than planned?
\end{itemize}

Firstly, if you are about to purchase an item \emph{earlier} than the (planned) end date, I suggest that you backdate its end date.
Otherwise the budget will penalize you in the month it was dated for purchase.
Seeing how this action, \ie purchasing item(s), is a not a monthly expense, the deviation for the month is the one that matters, not the one for the whole year.
Therefor, if you do not backdate the end, you will have created an unnecessary deviation in the month you actually purchase it.
But this will increase the monthly values for past months, and if your budget overall is arguably tight, it will possibly add strain to the months that already went by.
Also, you would be adding an amount of money to the already budgeted amount in the past months, which would be kind of fake as all kinds of expenses have been spent, all kinds of budget items were planned more or less carefully so that it all made sense from a financial perspective.
So that the past months might not be diluted by the fake 

If you end up not purchasing something in the right month, that is on you.
But that is ok and you could be happy about the positive effect on the deviation.

As mentioned \autoref{subsec:tracking-column-date}, there are 2 ways (at least the ones I listed) that dates can be used:
\begin{enumerate}
	\item A date for the day something was bought/ordered.
	Regardless of any kind of money transfer, this is the date the purchase was planned for.
	\item With regards to any kind of money transfer, there is also date--in case one uses some form of electronic payment (\eg a card)--on which the amount is actually transferred from your account.
\end{enumerate}

Finally, regardless of your actions or lack thereof, there is the time factor in the money transfer.
The debit could be withdrawn too late or too early from your account and by being the thorough tracker you certainly strive to be, you treat the dates as they occur in real life and ultimately have a unnecessary deviation, but it still happened: you could possibly have overdrawn your checking account or withdrawn an amount too late.
Well, that is life.
Regardless, you update your list to reflect your view. (because who does not like a well-maintained list, right??). \todo{punkt checken wegen einmal plan-datum und real datum}


However all that may be discussed further, you need to decide which path you take:
\begin{itemize}
	\item Shall budgeting in \tfn reflect real life or should \tfn not be changed and remain set to the planned to data?
	\item Should you wait with the purchase or set a calendar reminder of some sort next time?
\end{itemize}

\subsubsection{Thoughts on Delayed Budgeting}
\label{subsubsec:thoughts-delayed-budgeting}

Say one the following situation occurs:
\begin{itemize}
	\item It is the last day of the month.
	\item One would go on a spontaneous shopping trip.
	\item You know you have some certain, yet unspecified, amount to spend.
	\item One would spend that amount.
	\item When you open your version of \tfn the next time, it is the next month and you will see a deviation
\end{itemize}

The nice way of going on with this is what I would call \begriff{delayed budgeting}.
But this is not a \todo{fehlt}

\subsubsection{Thoughts on Deviations for Categories}
\label{subsubsec:thoughts-deviations-for-categories}

Ausführungen\todo{fehlt}
\begin{itemize}
	\item In general, the budget categories get summed and lumped together each month.
	\item One could argue that the budget categories should be 
	\item Dealing with (delayed) deviations can result in a double-edged sword:
	\begin{itemize}
		\item On one hand, it feels kind of ``good'' to have a surplus for a budget item.\\
		\ldots in case this happens often, this item is clearly budgeted
		\item On the other hand, 
		\item \ldots wrong.
	\end{itemize}
\end{itemize}

\subsection{Examples for Budgeting Expenses}
\label{subsec:examples-budgeting-expenses}

This subsection includes examples for showcasing how to use the budgeting sheets for expenses.
If you read through \autoref{subsec:budgeting-in-finances.ods} to \autoref{subsec:thoughts-on-budgeting}, lots of things and bits should be familiar and hopefully get cleared up if they are still a bit nebulous.

\subsubsection{Winter Coat}
\label{subsubsec:example-budgeting-expense-winter-coat}

For the example of budgeting a winter coat, let us take these facts \& figures into accounts:
\begin{itemize}
	\item We want to budget for the purchase of a super awesome winter coat which could cost up to with a value of 800\,€.
	\item It is March and it possible to buy the coat in October.
	Then the stores definitely have the new merchandise on the shelves.
\end{itemize}
The first columns in the row for that budget item could look like shown in \autoref{tab:example-budgeting-expense-winter-coat-dataentry}.
These entries yield the values shown in the gray columns in \autoref{tab:example-budgeting-expense-winter-coat-graycolumns}.\footnote{Of course the second table is directly to the right of the first one in the spreadsheet file.
I split them up to avoid for the sake of readability.}

\begin{table}[htbp]
	\centering
	\addtolength{\leftskip} {-2cm}
	\sffamily
	\caption[Example for Budgeting a Winter Coat: Data Entry]{Example for Budgeting a Winter Coat.
	The values from the bullet list above are displayed in the corresponding columns.}
	\label{tab:example-budgeting-expense-winter-coat-dataentry}
	\begin{tabular}{|c|l|c|c|c|c|c|c|l|}
		\hline
		\footnotesize\textbf{No.} & \rotatebox{0}{\footnotesize\textbf{Descr.}} & \rotatebox{0}{\footnotesize\textbf{Amount}} & \rotatebox{0}{\footnotesize\textbf{Start Date}} & \rotatebox{0}{\footnotesize\textbf{End Date}} & \rotatebox{0}{\footnotesize\textbf{Monthly Exp.}} & \rotatebox{0}{\footnotesize\textbf{Sum Prohib.}} & \rotatebox{0}{\footnotesize\textbf{Done}} & \rotatebox{0}{\footnotesize\textbf{Category}}\\ 
		\hline
		\hline
		1 & Winter Coat & 800 & 2019-03 & 2019-10 & 100 & No & No & Clothing/Acc.\\
		\hline
	\end{tabular}
\end{table}

\begin{table}[htbp]
	\centering
	\sffamily
	\caption[Example for Budgeting a Winter Coat: Data Entry]{Example for Budgeting a Winter Coat.
	The values from the bullet list above are displayed in the corresponding columns.}
	\label{tab:example-budgeting-expense-winter-coat-graycolumns}
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		\footnotesize\textbf{Cat.-No.} & \footnotesize\textbf{Months tot.} & \footnotesize\textbf{€/Month} & \footnotesize\textbf{Months in 2019} & \footnotesize\textbf{€ in 2019} & \footnotesize\textbf{Budgeted}\\
		\hline
		\hline
		\rowcolor{lightgray}
		001 & 8 & 100 & 8 & 800 & No\\
		\hline
	\end{tabular}
\end{table}

Now with \autoref{tab:example-budgeting-expense-winter-coat-graycolumns} in mind, let us circle back to \autoref{subsubsec:budgeting-item-column-sum-prohibition} and talk about its consequences for budgeting the winter coat.
As we have just read, we put 100\,€ into the virtual envelope\footnote{See \autoref{subsubsec:budgeting-the-envelope-method}.} per month.
This whole concept is displayed in \autoref{tab:bic-sum-prohibition-clarification}.\todo{ausarbeiten und mal sum prohibition aufzeigen?}

\begin{table}[htp]
	\centering
	\caption[Example for Sum Prohibition]{An Example for Sum Prohibition.
		The respective values }
	\label{tab:bic-sum-prohibition-clarification}
	\begin{tabular}{ccrr}
		\toprule
		\begin{minipage}[b]{1.0cm}
		Nr. of\\
		Month	
		\end{minipage}
		& \begin{minipage}[b]{1.4cm}
			Calendar\\
		 	Month	
		 \end{minipage}
		&
		\begin{minipage}[b]{2.25cm}
			Amount going\\
			to envelope	
		\end{minipage}
		 & 
		\begin{minipage}[b]{2.0cm}
			Total worth\\
			in envelope	
		\end{minipage}\\
%		\cmidrule(l{5.5pt}r{5pt}){2-2}
		\cmidrule(r){1-1}
		\cmidrule(lr){2-2}
		\cmidrule(lr){3-3}		
		\cmidrule(lr){4-4}
		1 & 2019-03 & 100 & 100\\
		2 & 2019-04 & 100 & 200\\
		3 & 2019-05 & 100 & 300\\
		4 & 2019-06 & 100 & 400\\
		5 & 2019-07 & 100 & 500\\
		6 & 2019-08 & 100 & 600\\
		7 & 2019-09 & 100 & 700\\
		8 & 2019-10 & 100 & 800\\
		\bottomrule
	\end{tabular}
\end{table}

\subsubsection{Utility: Water}
\label{subsubsec:example-budgeting-utility-water}

