\section{First Steps}
\label{sec:first-steps}
% !TeX spellcheck = en_US

\subsection{Introducing LibreOffice Calc}
\label{subsec:introducing-libreoffice-calc}

LibreOffice is a free office suite and great software.\footnote{See \href{https://www.libreoffice.org/discover/libreoffice/}{https://www.libreoffice.org/discover/libreoffice/}.}
You can download it on its   \href{https://www.libreoffice.org/download/download/}{official download page} of course.

Per \href{https://www.libreoffice.org/discover/calc/}{its official website}:
\begin{quote}\small
	Calc is the free spreadsheet program you've always needed. Newcomers find it intuitive and easy to learn, while professional data miners and number crunchers appreciate the comprehensive range of advanced functions. Built-in wizards guide you through choosing and using a comprehensive range of advanced features. Or you can download templates from the LibreOffice template repository, for ready-made spreadsheet solutions.
\end{quote}

\subsubsection{Help and Tips for LibreOffice Calc}
\label{subsubsec:help-tips-for-libreoffice-calc}

Providing help for working with \loc and writing a full introduction about it is clearly beyond the scope of this document.
I will, though, give thoughts on some key aspects I regard as crucial, but before that there are these important links and documents for proper help on \loc:
\begin{itemize}
	\item The most important bit first: \loc is not so different from Excel.
	Many things you might have picked up while working with Excel are certainly going to work in a similar--if not identical--way in Calc.
	\item The Official Documentation is really great.
	But even better is the \sterm{Getting Started} guide, which was released for LibreOffice 6 as well.\footnote{URL: \href{https://documentation.libreoffice.org/en/english-documentation/getting-started-guide/}{https://documentation.libreoffice.org/en/english-documentation/getting-started-guide/}.}
	Please start with pages 1--14, which are important overall, but especially important for Mac users.
	The actual good stuff is the section for Calc, which starts on page 118.
	\item By the way, if you are using Windows and Adobe Reader for reading PDF-files, you can quickly jump to any page with the keyboard shortcut \keystroke{Ctrl}+\keystroke{N}.
	In Evince on Linux, use \keystroke{Ctrl}+\keystroke{L}.
	\item For the sake of thoroughness, it is worth mentioning that you should  not ever hesitate to use \href{http://www.duckduckgo.com}{http://www.duckduckgo.com} and  \href{https://www.google.com}{https://www.google.com}.
\end{itemize}

\subsubsection{First Steps with LibreOffice Calc}
\label{subsubsec:first-steps-with-libreoffice-calc}

First of, here are some suggestions in terms of introductory videos:
\begin{itemize}
	\item Joel Spolsky's \sterm{You Suck at Excel} is some tongue-in-cheek take at teaching you Excel: \url{https://www.youtube.com/watch?v=0nbkaYsR94c}.\footnote{If you are not familiar with him, I recommend checking out his \href{https://en.wikipedia.org/wiki/Joel_Spolsky}{Wikipedia page} if you feel inclined to.}
	That video is really great and packs quite the punch for being only 54 minutes long.
	As stated in \autoref{subsubsec:help-tips-for-libreoffice-calc}, I am confident you will be able to transfer a lot of knowledge to \loc.
	\item A good video for strictly \loc is this: \url{https://www.youtube.com/watch?v=HcpaIuOLCqo}.
\end{itemize}

Here are some suggestions for first steps if you intend to follow through with learning how to work with \loc.
Again, you might be able to utilize knowledge you gained while working with Excel or Google Sheets.
To optimize your workflow  or generally increase your productivity with \tfn, you should definitely learn about the following keyboard shortcuts:
\begin{itemize}
	\item Copying content is done, as usual, with \keystroke{Ctrl}+\keystroke{C}.
	\item However, pasting in Calc can be done in multiple ways:
	\begin{enumerate}
		\item \keystroke{Ctrl}+\keystroke{V}: the well-known way.
		It will paste the content and adjust references to columns and/or rows.
		This keeps the content in cache and you can paste it again.
		\item Simply pressing Enter~/~\keystroke{\( \hookleftarrow \)}: simple and deleting cache.
		This does not keep the content in the memory cache.
		\item \keystroke{Ctrl}+\keystroke{Shift}+\keystroke{V}: the ``richest'' way and all the possible options are described here: \url{https://help.libreoffice.org/Common/Paste_Special}.
		If you copied the content in a spreadsheet file and use this keyboard shortcut, Calc will show a dialog window named \sterm{Paste Special}.\footnote{If you are working with Excel, use \keystroke{Ctrl}+\keystroke{Alt}+\keystroke{V}.}
		In this you can select the intended attributes of the paste action while simultaneously performing operations.
		With hitting \keystroke{\( \hookleftarrow \)} or clicking on \keystroke{Ok}, the copied content gets pasted to the currently marked cell.
		The content is kept in cache and you can paste it again.
	\end{enumerate}
	\item Deleting content, format-wise and content-wise, is done via \keystroke{\( \longleftarrow \)} (Backspace).
	A window will pop up and show you different selections.
	If you select \codestuff{Delete all}, all content and all formatting of the selected cell(s) will get deleted.
	\item For the case of copying/replacing cells in bulk, look at keyboard shortcuts on page 129 in \sterm{Getting Started}.
	For example, if a cell in a bigger group/block of cells is selected and you would like to additionally select all the cells to the right of the current cell in this block, use the shortcut \keystroke{Ctrl}+\keystroke{Shift}+\keystroke{\( \rightarrow \)}.
\end{itemize}

You should also definitely learn about \sterm{cell style templates} and the \sterm{navigator}:
\begin{itemize}
	\item Cell style templates are the core properties of formatting the whole thing.
	Without them, one would go crazy when editing \tfn (ok, I admit I am talking about me).
	The templates can be found in the stylist (press \keystroke{F11} for that), which enable you to make fast changes to the look (format-wise) of the file.
	Note: if you change one of them, you are changing the formatting of all cells in the entire document that have been formatted with this style template.
	And this effect is the intended behavior.
	\item About navigation:
	\begin{itemize}
		\item The navigator (reachable via \keystroke{F5}) enables you to navigate arguably fast between the sheets if you do not use keyboard shortcuts.
		It not only lists all visible sheets in the file, but also all other kinds of elements that can be found in it.
		\item Regardless of the navigator, you can cycle through the sheets via \keystroke{Ctrl}+\keystroke{Page Up} and \keystroke{Ctrl}+\keystroke{Page Down}.
	\end{itemize}
\end{itemize}

Lastly, I should say that after 6 months and the diligent tracking of each expense you made, the file takes notably longer to load and save.
At the end of the year, both actions take roughly 45-50 seconds on my main computer which is roughly 7 years old and has no SSD.

\subsection{Synchronization}
\label{subsec:synchronization}

Simply save the file in a folder which gets synchronized with some kind of (personal cloud) software, \eg Dropbox or whatever you would like to use.

\subsection{Security}
\label{subsec:security}

For securing the file, use the password-protection when you save it.
For more guidance on that, please consult the \sterm{Getting Started} guide, page 30.
An important note on this:
\begin{specialnote}
Do not lose the password!
\end{specialnote}

\subsection{Opening The File for The First Time and Starting Out}
\label{subsec:opening-the-file}

As you first open \tfn, you should navigate to the sheet \sheetname{2019total}.
Fill in the initial values into the cells in columns \codestuff{A} to \codestuff{E}.
Based on them, all future transactions, entries or budgeted values will make sense or not, so this should tell you how important it is that they are accurate.

The next steps are, not necessarily in this order:
\begin{enumerate}
	\item tracking
	\item budgeting
	\item analysis and controlling of your spending
\end{enumerate}

I regard the last point as somewhat obvious and not truly worthy of long explanations so I will not provide a fleshed-out section for that item.
In my humble opinion, it is probably the most inherent part of \tfn, as one simply must deal with all the numbers in the file and thus gains an analytical perspective on all the bits and pieces, at least in time.
Also, if you read the chapters on tracking and budgeting, you will definitely learn how to use \tfn's parts to improve.