\section{Miscellaneous Help}
\label{sec:miscellaneous-help}
% !TeX spellcheck = en_US

\subsection{Navigation by Hyperlinking Sheets}
\label{subsec:navigation-hyperlinking-sheets}

One way to speed up navigating through \tfn is using hyperlinks.
You can insert one by using the shortcut \keystroke{Ctrl}+\keystroke{K}.
Then, \ldots
\begin{itemize}
	\item if you had already selected some text, it will use that text as the descriptor text and give you the opportunity to paste a link into the target field or
	\item if you had nothing in the cache, you will have to enter both URL and the descriptor text.
\end{itemize}
\todo{verlinkungen im overview blatt}

If you intend to click on a link in \loc, \emph{first} hold \keystroke{Ctrl} and then click on it with your mouse.
You can change this setting in the options: Extra \structurenext Settings \structurenext LibreOffice \structurenext Safety \structurenext Options.

\subsection{Budgeted Items Which Are Due}
\label{subsec:budgeted-items-which-are-due}

The sheet \sheetname{BudgetShoppingList} serves as a shopping list.
You will find the following items listed:
\begin{itemize}
	\item the items which are budgeted and can be bought in the current month,
	\item the items which are to be fully budgeted in the next month and in the month after that and
	\item all the budgeted items which you bought in the past months.
\end{itemize}

Note: the formulas in this sheet utilize the \ac{bic} \sterm{Done} that shows if a budget item has been bought or its monthly expense has finished (see \autoref{subsubsec:bic-done}).

\subsection{Income and Spending over a Certain Time Period}
\label{subsec:income-and-spending-certain-time-period}

The sheet \sheetname{TimePeriod} is for showing you the sums of daily cash outflows and inflows for the given time period.

For that, you need to type out all the names of your tracking sheets in the table below.
Then you can enter the start date and end date for an arbitrary time period and it will show produce the values.

The only requirement is that you did do well on your tracking duties, other than there is not really a whole lot of magic involved.

\subsection{Tracking Special Budget Items or Special Expenses}
\label{subsec:tracking-special-expenses}

Circling back to the surplus amounts, I would like to introduce another utilization of them: the sheet for tracking of expenses which are special, relatively speaking.
If you want to, you can track your payments or saved amounts for certain goals or expenses in this sheet, \ie saving up 3000\,€.

Based on the data contained in this sheet, one could perhaps create or add a dashboard-like visualization in the sheet \sheetname{Overview}.

%Falls etwas überschuss da ist, kann man diesen theoretisch im nächsten monat extra verplanen! natürlich. nur wie möchte man den überblick halten, wenn man monatlich nach und nach stärker budgetiert, da man mehr mittel zu verfügung hat und dementsprechend verplanen kann?

\subsection{Prepare The Next Year and Analysis of Your Data}
\label{subsec:prepare-the-next-year-analysis}

Before you can move on to preparing \tfn for the next year, you should finalize the current/old file:
\begin{enumerate}
	\item Come December 31, the first ToDo-point on your list should be to save and close your current file.
	Then make a copy of it and rename it in regards to the new year, \eg to \emph{Finances-2020.ods}.
	\item Open your (still current) file and write down the last pieces of information in regards to the last day of the year.
	So literally write down \codestuff{2019-12-31} into any cell that prints today's date, \eg in the \sheetname{Budget} sheet.
	Also look for cells that print the current month or day and fill in \codestuff{2019-12} or \codestuff{31}.
	\item Proceed in an analogical fashion for every cell that prints dates through formulas.
	Otherwise the next time you open that file will be later than December 31 of that ``old'' year and the formulas which rely rather, they do not show values which make sense., the cell that prints the date of that day which will probably somewhere in January.
\end{enumerate}

\begin{itemize}
	\item Take a really close look at the \sheetname{Budget} sheet and analyze the outcomes of the deviations throughout the whole year.
	You should put a focus on the 
	\begin{itemize}
		\item Kategorien mit den großen Monatsstandard-Anteilen beackern\todo{weiter}
		\item basierend auf den Inhalten die neuen Monatsstandards gestalten
		\item hinweis: könnte quasi unmöglich sein, da sehr viele einzelne budget-items übereinandergelegt wurden
		\item bei der Analyse sollte auch berücksichtigt werden, dass das Budget einerseits mit und ohne Abweichung gleichzeitig ausgewiesen wird - das heißt, es werden auch vorgehaltene, noch weiterhin zu sparende Beträge ausgewiesen.
		\item alles aus einem Pot
	\end{itemize}	
	\item Finally, save the file.	
\end{itemize}

Then, close the file, copy it and rename it accordingly, \eg to \emph{Finances-2020.ods}.\todo{weiter}
Open that new file and
\begin{itemize}
	\item alle Inhalte löschen
	\item Datums-Formeln neu machen
	\item in den budget-blättern die monatsangaben ändern
\end{itemize}

\subsection{Forecasting}
\label{subsec:forecasting}

There is one other feature that I had originally planned to integrate: \emph{forecasting}.
Forecasting is the process of making predictions about future developments based on past and present data and most commonly by analysis of trends.\footnote{Cp. \href{https://en.wikipedia.org/wiki/Forecasting}{https://en.wikipedia.org/wiki/Forecasting}.}

I am not opposed to integrate more sheets and calculations into \tfn, but so far I have not used trends and honestly, I think I was able to deduce the good-enough optimizations of budgeted amounts by myself.
And as stated multiple times throughout this guide, the file spans over 12 months (only), which obviously makes it impossible to form average values which account for values spanning over a longer time period than 12 months.